A template for the *arxiv* style

### 2022-02-04 2-the-cubble-pkg.Rmd
make notes and small changes till section 4.2

Spatio-temporal data usually come in various forms and Figure \ref{fig:illu-input} shows four examples of this. No matter which form the data is in, these formats share some common components that characterise spatio-temporal data. A spatial identifier (`id` in the diagram) is the unique identifier of each site. The temporal identifier (`t` in the diagram) prescribes the time stamp each site is recorded. Coordinates, comprising of latitude and longitude (`lon` and `lat` in the diagram), locates each site on the map. These identifiers will be the building blocks for the data structure introduced below. Other variables in the data can be categorised into two groups: spatial variables that are invariant at each time stamp for every site, i.e. the name or code of the weather station and temporal variables that varies with time.

```{r illu-input, echo = FALSE, out.width = "100%", fig.cap="Illustration of incoming data formats for spatio-temporal data. (1) Data comes in as a single table; (2) Separate tables for spatial and temporal variables; (3) A single table with all the parameters used to query the database and a separate table for queried data; and (4) Cubical data in array or NetCDF format.", fig.align='center', out.height = "15%"}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.001.png"))
```

In a cubble, there are two forms: nested form and long form, and Figure \ref{fig:illu-cubble} sketches the two forms along with the associated attributes. The decision on which form to use is output-oriented, meaning analysts need to first think about whether the output of a particular operation is identified only by the spatial identifier, or a combination of spatial and temporal identifier. The nested cubble is suitable for working with operations that are only identified by site and this type of operation can be a pure manipulation of spatial variables, or a summary of temporal variables by site (i.e. the output of counting the number of raining day is only identified by sites and hence should be performed with the nested form). Underneath the nested form, a cubble is built from a row-wise dataframe (`rowwise_df`) where each site forms a separate group. This structure simplifies the calculation that involves temporal variables by avoiding the use of `map` syntax when working with list-column.

@@

To use functionalities from cubble, data analysts first need to create a cubble. `as_cubble` create a \pkg{cubble} by supplying the three key components: `key` as the spatial identifier; `index` as the temporal identifier; and a vector of `coords` in the order of longitude first and then latitude. The naming of `key` and `index` follows the convention in the \pkg{tsibble} package. The cubble created by default is in the nested form. Below is an example of creating a cubble: \newline

```{r}
(cubble_nested <- cubble::climate_flat %>%
  as_cubble(key = id, index = date, coords = c("long", "lat")))
```

There are a few information in the \pkg{cubble} header: the name of the `key` variable, bbox, and also the name of variable nested in the `ts` column. In this example, each site is identifier is `id` and the number in the bracket means there are 5 unique `id` in this dataset. The bbox in the second row gives the range of the coordinates. The temporal variables are all nested in the `ts` column, but it could be useful to know the name these variables. The third row in the cubble header shows these names and in this example this includes: precipitation, `prcp`, maximum temperature, `tmax`, and minimum temperature, `tmin`.

@@

```{r}
(cubble_long <- cubble_nested %>% stretch(ts))
```

Notice here that the third line in the header now shows the name of spatial variables rather than the temporal variables.

@@

Manipulation on the spatial and temporal dimension can be an iterative process. Many times, analysts will need to go back and forth between the nested and long cubble. The `stretch()` function introduced in the previous section switches a nested cubble into a long cubble and function `tamp()` is its inverse function to switch a long cubble back to the nested cubble:

```{r}
(cubble_back <- cubble_long %>% tamp())
```

@@

As a final data output for modelling or visualisation, spatio-temporal data is usually expected to be in a single table. Function `migrate()` moves the spatial variables from the `spatial` attribute into the long cubble:

```{r}
(cubble_long %>% migrate(long, lat))
```

In this workflow described above, data objects come into cubble in the nested form, then various operations on the spatial and temporal dimension can go back and forth between the nested and long form, and finally, the data will come out of cubble in the long form for further modelling or visualisation.

@@

```{=tex}
\begin{center}
\begin{tabular}{ | m{5em} | m{15cm}| } 
basics & \textbf{mutate}, \textbf{filter}, \textbf{summarise}, \textbf{select}, \textbf{arrange}, \textbf{rename}, \textbf{left\_join} \\
grouping &  \textbf{group\_by}, \textbf{ungroup}\\
slice family & \textbf{slice\_head}, \textbf{slice\_tail}, \textbf{slice\_sample}, \textbf{slice\_min} and \textbf{slice\_max} \\
\end{tabular}
\end{center}
```
\pkg{cubble} is also compatible with \pkg{tsibble} in the sense that the original list-column can be a `tbl_ts` object. Duplicates and gaps should be first checked before structuring the data into a cubble. If the input data is a \pkg{tsibble} object, the long form cubble is also a \pkg{tsibble} where users can directly apply time series operations.

>>>>

Spatio-temporal data usually come in various forms and Figure \ref{fig:illu-input} shows four examples of this. No matter which form the data is in, these formats share some common components that characterise the spatio-temporal data. A spatial identifier (`id` in the diagram) is the unique identifier of each site. The temporal identifier (`t` in the diagram) prescribes the time stamp each site is recorded. Coordinates, comprising of latitude and longitude (`lon` and `lat` in the diagram), locates each site on the map. These identifiers will be the building blocks for the data structure introduced below. Other variables in the data can be categorised into two groups: spatial variables that are invariant at each time stamp for every site, i.e. the name or code of the weather station, and temporal variables that varies with time.

```{r illu-input, echo = FALSE, out.width = "100%", fig.cap="Illustration of incoming data formats for spatio-temporal data. (1) Data comes in as a single table; (2) Separate tables for spatial and temporal variables; (3) A single table with all the parameters used to query the database and a separate table for queried data; and (4) Cubical data in array or NetCDF format.", fig.align='center', out.height = "40%"}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.001.png"))
```

In a cubble, there are two forms: nested form and long form, and Figure \ref{fig:illu-cubble} sketches the two forms along with the associated attributes. The decision on which form to use is output-oriented, meaning analysts need to first think about whether the output of a particular operation is identified only by the spatial identifier, or a combination of spatial and temporal identifier. The nested cubble is suitable for working with operations that are only identified by the site and this type of operation can be a pure manipulation of spatial variables, or a summary of temporal variables by site (i.e. the output of counting the number of raining day is only identified by sites and hence should be performed with the nested form). Underneath the nested form, a cubble is built from a row-wise dataframe (`rowwise_df`) where each site forms a separate group. This structure simplifies the calculation that involves temporal variables by avoiding the use of `map` syntax when working with list-column.

@@

\textcolor{red}{To use functionalities from cubble, data analysts first need to create a cubble.} `as_cubble()` creates a \pkg{cubble} by supplying the three key components: `key` as the spatial identifier; `index` as the temporal identifier; and a vector of `coords` in the order of longitude first and then latitude. The naming of `key` and `index` follows the convention in the \pkg{tsibble} package. The cubble created by default is in the nested form. Below is an example of creating a cubble: \newline

```{r echo = TRUE}
cubble_nested <- cubble::climate_flat %>%
  as_cubble(key = id, index = date, coords = c("long", "lat"))
cubble_nested
```

There are a few information in the \pkg{cubble} header: the name of the `key` variable (`id`) and its number (5), bounding box (`[115.97, -32.94, 133.55, -12.42]`), and also the name of variable nested in the `ts` column with its type (`date [date], prcp [dbl], tmax [dbl], tmin [dbl]`).

@@

```{r echo = TRUE}
cubble_long <- cubble_nested %>% stretch(ts)
cubble_long
```

Notice here that the third line in the header now shows the name and type of spatial variables (`lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id [dbl]`).

@@

Manipulation on the spatial and temporal dimension can be an iterative process. Many times, analysts will need to go back and forth between the nested and long cubble. `tamp()` inverses the `stretch()` that introduced in the previous section, to switch from a long cubble to the nested cubble:

```{r echo = TRUE}
cubble_back <- cubble_long %>% tamp()
cubble_back
```

@@

\textcolor{red}{As a final data output for modelling or visualisation, spatio-temporal data is usually expected to be in a single table.} Function `migrate()` moves the spatial variables from the `spatial` attribute into the long cubble:

```{r}
cubble_long %>% migrate(long, lat)
```

<!-- In the workflow described above, data objects come into cubble in the nested form, then various operations on the spatial and temporal dimension can go back and forth between the nested and long form, and finally, the data will come out of cubble in the long form for further modelling or visualisation. -->

@@

```{=tex}
\begin{center}
\begin{tabular}{ | m{5em} | m{15cm}| } 
basics & \textbf{mutate}, \textbf{filter}, \textbf{summarise}, \textbf{select}, \textbf{arrange}, \textbf{rename}, \textbf{left\_join} \\
grouping &  \textbf{group\_by}, \textbf{ungroup}\\
slice family & \textbf{slice\_head}, \textbf{slice\_tail}, \textbf{slice\_sample}, \textbf{slice\_min} and \textbf{slice\_max} \\
\end{tabular}
\end{center}
```

\pkg{cubble} is also compatible with \pkg{tsibble} where each element list-column in the nested form can be a `tbl_ts` object. \textcolor{red}{Duplicates and gaps should be first checked before structuring the data into a cubble.} If the input data is a \pkg{tsibble} object, the long form cubble is also a \pkg{tsibble} where users can directly apply time series operations. \textcolor{red}{more experiment with tsibble}

### 2022-02-04 3-advanced.Rmd
make notes and small changes till section 4.2

Spatial locations can have further grouping structure either in nature (i.e. countries are nested in continents), or calculated by some clustering algorithms. Rather than investigate the read from individual locations, group character summarised from multiple locations can give a clearer picture of the local dynamic. In cubble, `switch_key()` can be used to create a new level of grouping of spatial location by specifying a clustering variable. Figure \ref{fig:illu-hier} illustrates the relationship of cubbles at site and cluster level, in both the long and nested form. By specifying `cluster_nested <- station_nested %>% switch_key(key = cluster)`, the cubble re-defines the cubble key from `id` in `station_nested` to `cluster` in `cluster_nested`. All the spatial variables variant to `cluster` are now nested into a `.val` column and cluster level variables can be computed in the same fashion as station level variables in `station_nested`. Following the same principal of `stretch`, the long form cluster level cubble expands the time series variables with both indices: `cluster` and `id`. All the cluster level variables are stored separately for recovering the nested from from the long form.

```{r illu-hier, echo = FALSE, fig.align="center", out.width = "100%", fig.cap = "Relationship between the station and cluster level cubble in both long and nested form."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.003.png"))
```

@@

To be a valid pair of matching, the matched pair from different data sources need to

@@

The cubble structure fits in naturally with the interactive graphic pipeline discussed in the literature [@buja1988elements; @buja1996interactive;  @sutherland2000orca; @xie2014reactive; @cheng2016enabling]. Diagram \ref{fig:illu-interactive} illustrates how linking works with the two forms in a cubble, where a time series plot is created with the long cubble and a map is created with the nested cubble. When a user action is captured from the map, the site will be activated in the nested cubble. Then, the nested cubble will communicate to the long cubble to activate all the observations with the same `id`. The long cubble will then highlight the  activated series in the time series plot.

The linking is also available from the time series plot to the map. The selection on the time series is through selecting the point on the time series and once a point is selected, it will be activated in the long cubble. All the observations that share the same `id`,  either in the long and nested cubble, are then activated. This includes other points in the same time series in the long cubble and the corresponding observation of site in the nested cubble. These activated observations will then being reflected in the updated plots and Diagram \ref{fig:illu-interactive-2} in the Appendix illustrates this process.

@@

Glyph map [@Wickham2012-yr] plots the time series as single glyph on the map. 
<!-- Variation of glyph maps has been developed to visualise uncertainty in **Visumap** [@Lucchesi2021] and deal with irregular local grid [@Beecham2021-vk].  -->
In \proglang{R}, `GGally` implements the glyph map through the `glyphs()` function, which outputs a data frame with calculated position (`gx`, `gy`, `gid`) of each point on the time series given the major and minor xy variable using linear algebra (Equation 1 and 2 in @Wickham2012-yr). The data can then be piped into `ggplot` to create the glyph map:

@@

While this calculation can be seen as part of the `setup_data()` in a `ggproto`. A re-implementation of the glyph map as `GeomGlyph` has been made in `cubble` to create the glyph map with `geom_glyph`:

@@

Polar glyph map can be specify as a parameter, `polar = TRUE`, in the `geom_glyph()`, along with `width` and `height` in either absolute or relative value. Global and local scale can also be controlled by the parameter `global_rescale`, which default to `TRUE`. Reference box and line can be added with separate `geom_glyph_box()` and `geom_glyph_line()`.

>>>>

Spatial locations can have grouping structure that is either inherent to the data  (i.e. countries are nested in continents), or formed by clustering. Rather than analysing variables in the site level, summarised variables in the cluster level can give a clearer picture of \textcolor{red}{local dynamic}. In cubble, `switch_key()` can be used to create a new level of grouping of spatial location by specifying a clustering variable. Figure \ref{fig:illu-hier} illustrates the relationship of cubbles at site and cluster level, in both the long and nested form. \textcolor{red}{unify the use of site/ station}. By specifying `cluster_nested <- station_nested %>% switch_key(key = cluster)`, the cubble re-defines the cubble key from `id` in `station_nested` to `cluster` in `cluster_nested`. All the spatial variables variant to `cluster` are now nested into a `.val` column and cluster level variables can be computed in the same fashion as station level variables in `station_nested`. Following the same principal of `stretch`, the long form cluster level cubble expands the time series variables with both indices: `cluster` and `id`. All the cluster level variables are stored separately for recovering the nested from from the long form.

```{r illu-hier, echo = FALSE, fig.align="center",out.height="40%", out.width = "100%", fig.cap = "Relationship between the station and cluster level cubble in both long and nested form."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.003.png"))
```

@@

\textcolor{red}{refine the beginning.} To be a valid pair of matching, the matched pair from different data sources need to

@@

Cubble fits in naturally with the interactive graphic pipeline discussed in the literature [@buja1988elements; @buja1996interactive;  @sutherland2000orca; @xie2014reactive; @cheng2016enabling]. Diagram \ref{fig:illu-interactive} illustrates how linking works from the map to the time series with the two forms of a cubble. The map and time series plot is associated with the nested or long cubble respectively and when a user action is captured on the map, the site will be activated in the nested cubble (left). The nested cubble will communicate to the long cubble to activate all the observations with the same `id` (middle). The long cubble will then highlight the activated series in the time series plot (right).

The linking is also available from the time series plot to the map. The selection(s) on the time series is through selecting the point(s) on the time series and once a point is selected, it will be activated in the long cubble. All the observations that share the same `id` are then activated and this includes other points in the same time series in the long cubble and the corresponding observation of site in the nested cubble. These activated observations will then being reflected in the updated plots and Diagram \ref{fig:illu-interactive-2} in the Appendix illustrates this process.

@@

Glyph map [@Wickham2012-yr] plots the time series as single glyph on the map and in \proglang{R}, `GGally` implements the glyph map through the `glyphs()` function. The function construct a data frame with calculated position (`gx`, `gy`, `gid`) of each point on the time series using linear algebra (Equation 1 and 2 in @Wickham2012-yr). The data can then be piped into `ggplot` to create the glyph map as:

@@

A re-implementation of the glyph map as a ggproto `GeomGlyph` has been made in the `cubble` package so that the glyph map can be created with `geom_glyph()`:

@@

Polar glyph map can be specify as a parameter, `polar = TRUE`, in the `geom_glyph()`, along with `width` and `height` in either absolute or relative value. Global and local scale can be controlled by the parameter `global_rescale`, which default to `TRUE` for global scaling. Reference box and line can be added with separate `geom_glyph_box()` and `geom_glyph_line()`.

### 2022-02-04 4-1-basic.Rmd
make notes and small changes till section 4.2

Global Historical Climatology Network (GHCN) provides daily climate measures from stations across the world and the dataset `weatherdata::historical_tmax` extracts the historical maximum temperature recorded for `r nrow(weatherdata::historical_tmax)` Australian stations. The data `historical_tmax` is already presented as a cubble, with `id` as the key, `date` as the index, and `c("longitude", "latitude")` as the coordinates. Other variables include `elevation`, `name`, `wmo_id`, `first_year`, and  `last_year` in the nested form and `tmax` in the long form. This example compares the maximum temperature in two periods: 1971 - 1975 and 2016 - 2020 for stations in Victoria and New South Wales.

Stations in the two states can be subsetted on the station number: Australia GHCN station number starts with `ASN00` and followed by the [Bureau of Meteorology (BOM) station number](http://www.bom.gov.au/climate/cdo/about/site-num.shtml), where the 2nd and 3rd digit (7th and 8th in the GHCN number) denote the state a station belongs to. New South Wales stations start from 46 to 75 and Victoria stations then follow from 76 to 90. Extracting Victoria and New South Wales stations is a filter operation in the spatial dimension and hence is operated in the nested form:

@@

The five year window is chosen to remove the effect of a particular year and the historical period of 1971 - 1975 is used since all the stations have records from 1970. This following chunk filters on records in the two study periods and summarises the maximum temperature into monthly measure. `stretch()` is used to convert the nested form cubble into the long form for these operations:

```{r eval=  FALSE, echo = TRUE}
tmax <- tmax %>% 
  stretch() %>%
  filter(lubridate::year(date) %in% c(1971:1975, 2016:2020)) %>%
  mutate(month = lubridate::month(date), 
         group = as.factor(ifelse(lubridate::year(date) > 2015, 
                                  "2016 ~ 2020", "1971 ~ 1975"))) %>%
  group_by(month, group) %>%
  summarise(tmax = mean(tmax, na.rm = TRUE))
```

A data quality issue with GHCN data is that while the first and last year of each series is provided, years missing in this period is not reported. There are a few stations which don't have records during 1971 - 1975 and these stations are filtered out by examining whether the summarised `tmax` has a total of 24 months. This is again a station-wise operation and is operated in the nested form, which is switched to from the long form by  `tamp()`:

@@

Figure \ref{fig:basic-manip} shows the glyph map made with the data after the wangling above. One issue with this map is that the similar pattern shown from a few nearby stations around Sydney (151E, 34S) and New castle (152E, 33S) can be distracting. Aggregation is a useful technique to observe the general pattern of a collection of series and will be the topic of the next example.

```{r basic-manip, out.width="100%", out.height="70%", fig.cap="Glyph map of the mean maximum temperature by month for Victoria and New South Wales weather stations. On the top left corner is a detailed legend for station Cobar highlighted in the black box. Compared to 1971 - 1975,  the period 2016 - 2020 sees an increase of mean maximum temperature in spring and summer in Australia (end and beginning of the year). A larger increase during the first three months of the year is observed at stations with a lower latitude."}
knitr::include_graphics("figures/basic-manip.png")
```

>>>>

Global Historical Climatology Network (GHCN) provides daily climate measures from stations across the world and the dataset `weatherdata::historical_tmax` extracts the maximum temperature for `r nrow(weatherdata::historical_tmax)` Australian stations. All the stations start recording from year `r range(weatherdata::historical_tmax$first_year)[2]` with the longest back to year `r range(weatherdata::historical_tmax$first_year)[1]`. The data `historical_tmax` is already presented as a cubble, with `id` as the key, `date` as the index, and `c("longitude", "latitude")` as the coordinates. This example compares the maximum temperature in two periods: 1971 - 1975 and 2016 - 2020 for stations in Victoria and New South Wales.

Stations in the two states can be subsetted on the station number: Australia GHCN station number starts with "ASN00" and followed by the [Bureau of Meteorology (BOM) station number](http://www.bom.gov.au/climate/cdo/about/site-num.shtml), where the 2nd and 3rd digit (7th and 8th in the GHCN number) define the state of the station. New South Wales stations start from 46 to 75 and Victoria stations follow from 76 to 90. Filtering Victoria and New South Wales stations is an operation in the spatial dimension and hence uses the nested form:

@@

Filtering for the period 1971: 1975 and 2016:2020 is an operation on the time dimension and the nested cubble needs to be switched to the long cubble by `stretch()`:

```{r eval=  FALSE, echo = TRUE}
tmax <- tmax %>% 
  stretch() %>%
  filter(lubridate::year(date) %in% c(1971:1975, 2016:2020)) 
```

A monthly average is used for both periods to smooth the maximum temperature and it is again an operation on the time dimension:

```{r eval=  FALSE, echo = TRUE}
tmax <- tmax %>%
  mutate(month = lubridate::month(date), 
         group = as.factor(ifelse(lubridate::year(date) > 2015, 
                                  "2016 ~ 2020", "1971 ~ 1975"))) %>%
  group_by(month, group) %>%
  summarise(tmax = mean(tmax, na.rm = TRUE))
```

There are a few stations which don't have records during 1971 - 1975 and further investigation shows that while the first and last year of each series is recorded, the missing years in this period is not reported. These stations are filtered out by examining whether the summarised time series has a total of 24 months. The long cubble needs to be switched to the nested form for this spatial operation using `tamp()`:

@@

`tmax` can then be supplied to `geom_glyph()` for the glyph map in Figure \ref{fig:basic-manip} with a station inset on the top left corner:

```{r eval = FALSE, echo = TRUE}
nsw_vic <- ozmaps::abs_ste %>% 
  filter(NAME %in% c("Victoria", "New South Wales"))

ggplot() + 
  geom_sf(data = nsw_vic, 
          fill = "transparent", color = "grey", linetype = "dotted") + 
  geom_glyph(data = tmax, 
             aes(x_major = longitude, x_minor = month, 
                 y_major = latitude, y_minor = tmax,
                 group = interaction(id, group), color = group),
             width = 1, height = 0.5) +
  ...
```

```{r basic-manip, out.width="100%", out.height="70%", fig.cap="A glyph map of the mean maximum temperature by month for Victoria and New South Wales weather stations in Australia. On the top left corner is an insetted plot of station Cobar, which is highlighted in the black box."}
knitr::include_graphics("figures/basic-manip.png")
```

### 2022-02-04 4-2-agg.Rmd
make notes and small changes till section 4.2

There are `r nrow(weatherdata::climate_full)` stations that record daily precipitation in Australia and these series will overlay on top of each other in a glyph map. Aggregation can be helpful to group series into clusters before visualising the cluster with glyph map. This example shows how to organise data at both level with the cubble function `switch_key()`.

A simple kmean algorithm based on the distance matrix is used here to create 20 clusters. This creates `station_nested` as a station level nested cubble with a cluster column indicating which group each station belongs to. More complex algorithms can be used for other problem, as long as there is a mapping from each station to a cluster.

@@

```{r echo = TRUE}
station_nested
```

>>>>

In the previous example, there has already been some overlapping of the glyphs for a few stations near (151E, 34S) and (152E, 33S) and this will be a problem when mapping more stations in the national level. Aggregation can be helpful to group series into clusters before visualising the cluster with glyph map.

This example shows how to organise data at both level with `switch_key()`. The dataset used is `weatherdata::climate_full`, which records daily precipitation and maximum/ minimum temperature for `r nrow(weatherdata::climate_full)` stations in Australia from 2016 to 2020. A simple kmean algorithm based on the distance matrix is used here to create 20 clusters. This creates `station_nested` as a station level nested cubble with a cluster column indicating the group each station belongs to. More complex algorithms can be used for other problem, as long as there is a mapping from each station to a cluster.

@@

```{r echo = TRUE, eval = FALSE}
station_nested <- weatherdata::climate_full %>% 
  mutate(cluster = ...)
```

### 2022-02-04 main.Rmd
make notes and small changes till section 4.2

---
documentclass: jss
author:
  - name: H. Sherry Zhang
    # department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    #location: Melbourne, Australia
    email: \email{huize.zhang@monash.edu}
  - name: Dianne Cook
    # department: Department of Econometrics and Business Statistics
    affiliation: 'Monash University \AND'
    # location: Melbourne, Australia
    # email:  dicook@monash.edu
  - name: Ursula Laa
    # department: Institute of Statistics
    affiliation: 'University of Natural Resources and Life Sciences \AND'
    # location: Vienna, Austria
    # email:  ursula.laa@boku.ac.at
  - name: Nicolas Langrené
    # department: 34 Village Street, Docklands VIC 3008 Australia
    affiliation: 'CSIRO Data61 \AND'
    # location: Melbourne, Australia
    # email: nicolas.langrene@csiro.au
  - name: Patricia Menéndez
    # department: Department of Econometrics and Business Statistics
    affiliation: 'Monash University \AND'
    # location: Melbourne, Australia
    # email:  patricia.menendez@monash.edu
title:
  formatted: "\\pkg{cubble}: An R Package for Structuring Spatio-temporal Data"
  # If you use tex in the formatted title, alsoge supply version without
  plain:     "cubble: An R Package for Structuring Spatio-temporal Data"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [spatio-temporal data,  "\\proglang{R}"]
  plain:     [spatio-temporal data, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
output: rticles::jss_article
bibliography: references.bib
---

>>>>

---
documentclass: jss
author:
  - name: H. Sherry Zhang
    # department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    #location: Melbourne, Australia
    email: \email{huize.zhang@monash.edu}
  - name: Dianne Cook
    # department: Department of Econometrics and Business Statistics
    affiliation: 'Monash University \AND'
    # location: Melbourne, Australia
    # email:  dicook@monash.edu
  - name: Ursula Laa
    # department: Institute of Statistics
    affiliation: 'University of Natural Resources and Life Sciences \AND'
    # location: Vienna, Austria
    # email:  ursula.laa@boku.ac.at
  - name: Nicolas Langrené
    # department: 34 Village Street, Docklands VIC 3008 Australia
    affiliation: 'CSIRO Data61 \AND'
    # location: Melbourne, Australia
    # email: nicolas.langrene@csiro.au
  - name: Patricia Menéndez
    # department: Department of Econometrics and Business Statistics
    affiliation: 'Monash University \AND'
    # location: Melbourne, Australia
    # email:  patricia.menendez@monash.edu
title:
  formatted: "\\pkg{cubble}: An R Package for Structuring Spatio-temporal Data"
  # If you use tex in the formatted title, alsoge supply version without
  plain:     "cubble: An R Package for Structuring Spatio-temporal Data"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  Sptio-temporal data naturally has two levels of observations: site and time level. [problem]. In this paper, a new data structure, `cubble`, is proposed for manipulating and visualising spatio-temporal data.
keywords:
  # at least one keyword must be supplied
  formatted: [spatio-temporal data,  "\\proglang{R}", climate data]
  plain:     [spatio-temporal data, R, climate data]
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
  \usepackage{xcolor}
output: rticles::jss_article
bibliography: references.bib
---
